Dynastic Extinctions and Urban Economic Development: \\Evidence from the Holy Roman Empire\footnote{I thank Davide Cantoni, Matthias Weigand, and my RA colleagues at the Chair of Economic History for helpful comments and feedback.}

### 2023-06-24 paper/paper.tex
#27 all figures and table are in

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.4]{paper/output/regressions/SW22_replication_50y.png}
    \caption{It looks just like it's supposed to!}
    \label{fig:SW_replication}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.15]{paper/output/descriptive/map_conflict_NA_50y.png}
    \caption{Share of observations remaining from each \textit{Städtebuch} region when controlling for conflict incidents in Equation \eqref{eq:baseline}. Geo-referenced borders of the regions were not available; this makeshift visualisation shows convex hulls of the city locations in each region (which results in some overlap.)}
    \label{fig:conflict_map}
\end{figure}

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.4]{paper/output/regressions/SW22_replication_50y.png}
    \caption{Dynamic effects of switching to another state. Coefficient estimates from Table \ref{eq:sw22}, Column (1). The outcome variable is the probability that construction activity of any type is observed in the period. The period beginning 50 years before the switch is omitted.}
    \label{fig:SW_replication}
\end{figure}

\begin{figure}[ht]
    \centering
    \includegraphics[scale = 0.15]{paper/output/descriptive/map_conflict_NA_50y.png}
    \caption{Share of observations remaining from each \textit{Städtebuch} region when controlling for conflict incidents in Equation \eqref{eq:baseline}. Note that this map shows fewer cities than Figure \ref{fig:map_cities} because Figure \ref{fig:map_cities} was produced from the full dataset, while this map only plots cities that satisfy the baseline sample restrictions.}
    \label{fig:conflict_map}
\end{figure}
